\ourtitle

### 2020-05-22 paper/article.tex
Prepare paper for submission

\author{Pedro M. Silva}{Dummy University Computing Laboratory, Portugal \and My second affiliation, Country \and \url{http://www.myhomepage.edu} }{johnqpublic@dummyuni.org}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}

@@

\keywords{Umbundu, Angola Languages, Morphological Analysis, Spell Checking}

%\funding{This research was partially funded by Portuguese National funds
%(PIDDAC), through the FCT – Fundação para a Ciência e Tecnologia and
%FCT/MCTES under the scope of the projects UIDB/05549/2020 and
%UIDB/00319/2020.  Bernardo Sacanene acknowledges from the Angolan
%govenment his PhD grant, through INAGBE (Instituto Nacional de Gestão
%de Bolsas de Estudos).}

>>>>

\author{Pedro M. Silva}{Departamento de Informática, Universidade do Minho, Braga, Portugal}{pg38423@alunos.uminho.pt}{https://orcid.org/0000-0002-1825-0097}{}

@@

\keywords{Domain Specific Language, Music Notation, Interpreter, Programming Language}
